\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-17 article.tex
resize fig
re-wrote presentation fo the paper

\textcolor{red}{It may be useful to rewritte the following lines but I add it to not forget about a plan (request from AQ)}
In section \ref{sec:filter}, we will describe how we filter the fluorescent calcium imaging signal.
In section \ref{sec:inference}, we will characterize our algorithm from a theoretical point of view.
In section \ref{sec:results}, we will present some results and give a critical comparision with other inference methods.
In appendix \ref{app:optimized}, we describe a fully tuned version of our algorithm which has won the Connectomics challenge.

@@

\begin{figure}[bth]
\centering
\includegraphics[width=0.8\linewidth]{images/fig_filtering}
\caption{Filtering steps.}
\label{fig:filtered-signal}
\end{figure}

@@

\section{Conclusion}

>>>>

The rest of the paper is structured as follows: Section \ref{sec:filter}
describes the pre-processing applied on fluorescent calcium timeseries;
Section \ref{sec:inference} presents the proposed approach and
their theoretical properties; Section \ref{sec:results} provide
empirical analysis and comparison with other network inference method,
whereas Section \ref{sec:conclusion} discusses our work and provides further
research directions.

@@

\begin{figure}[bth]
\centering
\includegraphics[width=0.4\linewidth]{images/fig_filtering}
\caption{Filtering steps.}
\label{fig:filtered-signal}
\end{figure}

@@

\section{Conclusion} \label{sec:conclusion}
